Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-30 paper/aldebaran.tex
wording

Using Eq \ref{eqn:numax} with the values in Table \ref{tab:spec} predicts $\nu_{\textrm{max}}$ in the range $0.5-6\mu$Hz. Reversing the equation to produce a predicted $\log{g}$ from the observed $\nu_{\textrm{max,obs}}=2.23\pm0.1\mu$Hz results in a predicted $\log{g}\sim1.2$ dex, using an assumed temperature of 3900K. The solar calibration values used here are $g_{\odot}=274$ms$^{-2}$, $\nu_{\textrm{max},\odot}=3150\mu$Hz and $T_{\textrm{eff},\odot}=5777$K.

@@

We have also investigated running \textsc{PARAM} and relaxing one or more constraints: without the luminosity constraint, the average absolute mass offset between the two sets of results was $<0.04\textrm{M}_{\odot}$ for the runs without $\nu_{\textrm{max}}$ constraint, and $<0.02\textrm{M}_{\odot}$ for the runs with $\nu_{\textrm{max}}$.

>>>>

Using Eq \ref{eqn:numax} with the values in Table \ref{tab:spec} predicts $\nu_{\textrm{max}}$ in the range $0.5-6\mu$Hz. Reversing the equation to produce a predicted $\log{g}$ from the observed $\nu_{\textrm{max,obs}}=2.23\pm0.1\mu$Hz results in a predicted $\log{g}\sim1.2$ dex, using an assumed temperature of 3900K. The solar calibration values used here are $g_{\odot}=274\,$ms$^{-2}$, $\nu_{\textrm{max},\odot}=3150\,\mu$Hz and $T_{\textrm{eff},\odot}=5777\,$K.

@@

We have also investigated running \textsc{PARAM} and relaxing one or more constraints: between runs with and without the luminosity constraint, the average absolute mass offset between the two sets of results was $<0.04\textrm{M}_{\odot}$ if we also ignore the $\nu_{\textrm{max}}$ constraint, and $<0.02\textrm{M}_{\odot}$ including the $\nu_{\textrm{max}}$.
